\begin{thebibliography}{99}

\bibitem{A} F.\ R.\ Adler, {\bfseries Modeling the Dynamics of Life:
Calculus and Probability for Life Scientists}, Brooks/Cole, 2005.

\bibitem{BE} D. Betounes, {\bfseries Partial Differential Equations for
Computational Science}, Springer-Verlag, 1998.

\bibitem{BC} R. L. Borelli et C. S. Coleman,
{\bfseries Differential Equations, a Modeling Perspective}, Wiley, 1998.

\bibitem{BR} M. Braun, {\bfseries Differential Equations and their
Applications, 4$^{th}$ edition}, Springer-Verlag, 1993.

\bibitem{LC} L. Carroll, {\bfseries Alice's Adventures in Wonderland},

\bibitem{FL} G. B. Folland, {\bfseries Advanced Calculus}, Prentice Hall, 2002

\bibitem{I} R. Illner, C. S. Bohun, S. McCollum et T. an Roode,
{\bfseries Mathemtical Modelling: A Case Studies Approach}, AMS, 2005.

\bibitem{SL} S. Lipschutz, {\bfseries Linear Alegebra}, Schaum's Outline
  Series, McGraw-Hill, 1968.

\bibitem{MT} J. E. Marsden and A. J. Tromba, {\bfseries Vector
 Calculus, 2$^{nd}$ edition}, W. H. Freedman and Company, 1981.

\bibitem{M} J. D. Murray, {\bfseries Mathematical Biology, 1: An
Introduction, 3$^{th}$ edition}, Springer-Verlag, 2002.

\bibitem{NH} C. Newhouser, {\bfseries Calculus for Biology and
Medecine 2$^{nd}$ Edition}, Prentice Hall, 2004

\bibitem{ND} B. Noble and J. W. Daniel, {\bfseries Applied Linear Algebra},
3$^{rd}$ edition, Prentice-Hall, 1988.

\bibitem{O} M. Olinick, {\bfseries An Introduction to Mathematical Models in
the Social and Life Sciences}, Addison-Wesley, 1978

\bibitem{R} D. A. Roff, {\bfseries The Evolution of Life Histories},
Chapman and Hall, 1992

\end{thebibliography}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "notes"
%%% End:
